Conflict Driven Evolution and Urban Development: \\ Evidence from the Holy Roman Empire\footnote{ I thank Lara Andermann, Leonie Bielefeld, Daniel Bursian, Davide Cantoni, Emilio Esguerra, Filip Milojevic, Johannes Vorbach and Matthias Weigand for helpful comments and feedback. }

### 2023-06-27 paper/paper.tex
#31 finish conclusion on PERIOD

Better understanding how the European state system evolved can deepen our understanding of social and economic history and of the origins of efficient institutions.

>>>>

While the research question may not seem hugely relevant for the present-day Western world, I want to close, briefly, with the Democratic Republic of the Congo (DRC). This African state's central government is weak and large parts of its territory are controlled by independent armed groups \citep[p. 34]{sierra2020}. Recent research has studied the DRC to investigate questions about state formation \citep{sierra2020}, taxation and state capacity \citep{balan2022}, and conflict \citep{henn2021}. One could argue that we are witnessing economic history "in real time" there.\footnote
{
This thought is not my own; Davide Cantoni said it to me in conversation.
} 
My point is that a better understanding of how the European state system evolved may not only deepen our knowledge of the origins of institutions --- it could also inform our perspective on regions of the world that do not have a stable state system at present.
